\textbf{Emergency Service Location Optimization in a Multi-Zone County based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
Edits

\subsection{Zone-to-Zone Population Dynamics}
The population that an ambulance can cover in a second zone, B, from a first zone, A, will be referred to as zone-to-zone coverage. Zone-to-zone coverage also applies if A and B are the same zone, and represents the coverage of an ambulance in the zone it is stationed in.

@@

%TODO: We are trying to find zone-to-zone coverage...

\begin{description}
    \item[$\mathbf{Z_{AB}(t)}$] \hfill \\
    	The zone-to-zone coverage function of B from A
    \item[$\mathbf{A(t), B(t)}$] \hfill \\
    	Probability density functions with respect to travel time from the center of A
    \item[$\mathbf{v}$] \hfill \\
    	Required ambulance response time
    \item[$\mathbf{T_{AB}}$] \hfill \\
    	Travel time from A to B, given
    \item[$\mathbf{T_{BA}}$] \hfill \\
    	Travel time from B to A, given
    \item[$\mathbf{P_B}$] \hfill \\
    	Total population of B
    \item[$\mathbf{F_B(s)}$] \hfill \\
    	The probability curve for differences in travel time within B
   \item[$\mathbf{T_A}$] \hfill \\
    	Average travel time inside of A
    \item[$\mathbf{T_{A+}}$] \hfill \\
    	Average travel time in the direction of B to A inside of A
    \item[$\mathbf{T_{A-}}$] \hfill \\
    	Average travel time in the direction of A to B inside of A
   \item[$\mathbf{T_B}$] \hfill \\
    	Average travel time inside of B
    \item[$\mathbf{T_{B+}}$] \hfill \\
    	Average travel time in the direction of A to B inside of B
    \item[$\mathbf{T_{B-}}$] \hfill \\
    	Average travel time in the direction of B to A inside of B
    \item[$\mathbf{a, b}$] \hfill \\
    	Width of A and B respectively
    \item[$\mathbf{g}$] \hfill \\
    	Width of the gap between A and B
\end{description}

%TODO: Graphical representation of origin and setup
% Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution

>>>>

\subsection{Zone-to-Zone Population Dynamics}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3.5in]{6point.pdf}
\caption{A graph of the nodes (zones) and edges (travel times).}
\label{satan1}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3.5in]{greedy6point.pdf}
\caption{A graph of the nodes (zones) with all edges (travel times) greater than 8 removed.}
\label{satan2}
\end{center}
\end{figure}

The population that an ambulance can cover in a second zone, B, from a first zone, A, will be referred to as zone-to-zone coverage. Zone-to-zone coverage also applies if A and B are the same zone, and represents the coverage of an ambulance in the zone it is stationed in.

Because we have more than four different zones, it is not possible for every zone to be adjacent with all the other zones. Therefore, the ambulance may travel through another zone C in an optimal route between zones A and B. However, we are only calculating the zone-to-zone population coverage of B from A, we can consider any time spent in zone C as a gap (i.e. containing a population density of 0). The zone-to-zone coverage of C from A is already accounted for in a separate calculation of A to C.

The following calculations are used to find the coverage function for any pair of zones. Separate calculations must be done for every pair, as we as for both directions for each pair. We will be using the following variables, equations, and constants:

\begin{description}
    \item[$\mathbf{Z_{AB}(t)}$] \hfill \\
    	The zone-to-zone coverage function of B from A; to be solved
    \item[$\mathbf{B(t)}$] \hfill \\
    	Probability density function of zone B with respect to travel time (from the center of A)
   \item[$\mathbf{a, b}$] \hfill \\
    	Width of A and B respectively
    \item[$\mathbf{v}$] \hfill \\
    	Required ambulance response time; given (8 minutes)
    \item[$\mathbf{T_{AB}, T_{BA}}$] \hfill \\
    	Travel time from A to B and travel time from B to A; given
    \item[$\mathbf{P_B}$] \hfill \\
    	Total population of B; given
   \item[$\mathbf{T_B}$] \hfill \\
    	Average travel time inside of B; given
    \item[$\mathbf{T_{B+}, T_{B-}}$] \hfill \\
    	Average travel time inside of B in the direction of A to B\\Average travel time inside of B in the direction of B to A
    \item[$\mathbf{F_B(s)}$] \hfill \\
	  Frequency distribution of travel times from one random point in zone B to another point in B
\end{description}
